Model Optimization

### 2015-01-29 Figure 6/abxD01.optimizingModel.Rmd
worked on modeling

>>>>

I wanted to use the information in the titration data set to improve the model. The original model was really good at predicting high levels of *C. difficile*, but not very good at lower levels. The titration data set includes groups with lower levels of *C. difficile*. So I'm running random forest with the titration data alone:

``` {r, eval=TRUE}
#################################
###rf of the titration data
rf.titr<-read.csv("~/Desktop/mothur/abxD01/rf/abxD01.final.an.unique_list.0.03.subsample.0.03.pick.shared.rf.newtitration.regression.logtrans.filter16mintot.noUntr.csv", header=T)
rf.titr<-rf.titr[,-1]

#fit the randomforest model
rf.titr.model <- randomForest(nextDayCFU~., 
                               data = rf.titr,  outscale=TRUE,
                               importance=TRUE, proximity=TRUE,
                               keep.forest=TRUE, ntree=5000
)
plot(rf.titr.model)
print(rf.titr.model)

#what are the important variables (via permutation) #type 1 is mean decrease in accuracy, type 2 is mean decrease in node impurity
varImpPlot(rf.titr.model, type=1)
imp<-importance(rf.titr.model)
most.imp<-rownames(imp[order(imp[, "%IncMSE"], decreasing=T)[1:17],])

The % variance explained was 90.95. Otu13, followed by 3 and 1 were the most obvious influences on the model.

I've also performed this same script to a file without the untreated titration groups. This yields 82.69% variance explained.  Otu3 is the most important OTU in this dataset, followed by 13, 1, 20, 42. In fact all the top OTUs are mostly porphyromonadaceae, a lachnospiraceae, and alistipes. It almost seems from this data like resistance is more about the loss of these protective bugs as opposed to growth of *C. difficile* promoting bacteria.
